Analysis of bulk void regions

### 2014-04-28 time-machine/cosmic_voids(24-04-14).tex
time machine

Following the recent growing interest in studying galaxy formation in 
low-density regions as cosmological tests, we use a simple method based on 
a FOF-like algorithm, where we build an input catalogue for the FOF method
with the coordinate of the center of every cell marked as void according 
to the web classification scheme adopted, setting a linking length to 
connect diagonal neighbour cells. Then, following the work of 
\SRKED{Forero-Romero et al. 2008}, we perform a percolation analysis in 
order to select the best threshold parameter that reduces percolation in 
cells.

In figure \ref{fig:percolation_analysis_FOF} we show the result of our 
percolation analysis for both web schemes. In both cases, it can be 
noticed that the volume of the largest void region in the lower panel is 
minimized at $\lambda_{th} = 0$, what means that percolation is completely 
reduced for this threshold value. Regarding the number of voids, shown in 
the upper panel, the T-web scheme presents a expected behaviour, where the 
number of voids decreases with \lth as the largest void absorbs minor 
voids through percolation. For the V-web scheme, there is an anomaly 
around the optimal \lth value, where there is a considerable increment of 
the number of voids. In the figure \ref{fig:volume_distributions}, we 
calculate a distribution function of the volume of voids. First for 
$\lambda_{th}=0.0$ in the upper panel, where both schemes present similar 
distributions, although voids in the V-web scheme are slight biased 
towards middle volume, with a lower abundance for low volume regions than 
voids in the T-web scheme. Secondly, in the lower panel of this figure, we 
compute the same distribution of volumes for the optimal parameter 
previously established for both schemes. Here, it can be noticed a 
significant over-abundance of low volume voids for the V-web scheme 
compared with the T-web. As it was above-mentioned from the figure 
\ref{fig:typical_mass_velocity}, the \lth value can be associated, at 
least indirectly, to an increase of the threshold value of the peculiar 
velocity field, in the case of the V-web, or the density field for the 
T-web. Therefore, the over-abundance of low volume voids for the V-web 
implies high fluctuations in the peculiar velocity field, while the 
density field is more robust. In the same plot, it can be noticed a lack 
of high volume voids, what is also due to percolation, since high volume 
voids are absorbed by the largest void.

In the light of the previous results, we choose a threshold parameter 
$\lambda_{th} = 0$ for all subsequent analysis of voids in order to avoid
percolation and high fluctuations of the V-web scheme. In spite of this 
value is quite different to the previously established optimal threshold
for each scheme, bulk voids for $\lambda_{th} = 0$ are expected to be 
the central cores of bulk voids at higher threshold values, assuming that 
percolation could be reduced. Therefore, global properties of voids are 
expected to maintain for $\lambda_{th} = 0$.

%*************************************************************************
\section{Properties of voids}
\label{sec:properties}
%*************************************************************************

Once defined the proper scheme to classify bulk voids in the simulation,
we proceed to analyse their physical properties, like the inertia values,
the density and peculiar velocities profiles as calculated over the grid 
and profiles of number of halos.

%-------------------------------------------------------------------------
\subsection{Shape of voids}
\label{subsec:shape_voids}
%-------------------------------------------------------------------------

Quantifying the shape of voids is gaining importance due to cosmological 
tests such as the Alcock-Paczynski test \SRKED{Sutter, et.al (2012)}, so 
we compute here the reduced inertia tensor through the next expression in 
order to determine shape distributions of bulk voids.

%.........................................................................
%Reduced inertia tensor
\eq{ReducedIntertia}
{ \tau_{ij} = \sum_l \frac{ x_{l,i}x_{l,j}  }{R_l^2} }
%.........................................................................
where $l$ is an index associated to each cell of the current region, 
$i$ and $j$ indexes run over each spatial direction and finally 
$R_l$ is defined as $R_l^2 = x_{l,1}^2 + x_{l,2}^2 + x_{l,3}^2$. All 
positions are measured from the respective geometric center of each void.

The eigenvalues of the reduced inertia tensor, i.e. the principal moments
of inertia, are used to quantify the shape of each bulk void. They are 
denoted as $\tau_1$, $\tau_2$ and $\tau_3$ such that $\tau_1 \leq \tau_2
\leq \tau_3$. In Figure \ref{fig:distro_inertia} we show the computed
distributions for $\tau_1/\tau_2$ and $\tau_2/\tau_3$ for voids larger 
than 8 cells in order to avoid statistic fluctuations due to small regions.
We rather calculate histograms for these ratio quantities instead of each 
single value in order to avoid using an arbitrary normalization. For both 
schemes, it can be noticed that the shape distribution is completely 
spread out, thereby indicating a non-preferred geometry of void regions, 
which is in agreement with the well established high anisotropy of matter 
flows associated to this type of region.

For a better quantification, we also perform a classification of the shape 
of voids by setting a threshold in the analysed ratio quantities. An 
anisotropic or tri-axial shape correspond to voids where $\tau_1/\tau_2 < 
0.7$ and $\tau_2/\tau_3 < 0.7$, where there is not any symmetry among the
principal directions. We find about $57.2\% \sim 61.0\%$ of total voids 
consistent with this shape, for the T-web and V-web respectively. A 
pancake or quasi-oblate shape is associated to voids where $\tau_1/\tau_2 
< 0.7$ and $\tau_2/\tau_3 > 0.7$. We found $13.1\% \sim 17.9\%$ of 
consistent voids. Filamentary or quasi-prolate voids satisfy $\tau_1/\tau_2 
> 0.7$ and $\tau_2/\tau_3 < 0.7$, with $25.4\% \sim 18.1\%$ of all voids.
Finally, isotropic or quasi-spheric voids are found when $\tau_1/\tau_2 
> 0.7$ and $\tau_2/\tau_3 > 0.7$, with $4.2\% \sim 3.1\%$ of total voids 
compatible with this shape. The threshold value of $0.7$ adopted here for
the ratios of the moments of inertia is just for illustrative purposes, 
where such distinction is rather fuzzy and continuous. However, the 
previous analysis allows us to conclude that voids are quite asymmetric 
structures.

%-------------------------------------------------------------------------
\subsection{Density profile of voids}
\label{subsec:density_voids}
%-------------------------------------------------------------------------

@@

%.........................................................................
%FIGURE 1: Fraction of halos in each environment
\begin{flushleft}
\begin{figure*}
\centering

@@

@@

  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_regions_percolation_FOF.pdf}

@@

%.........................................................................
%FIGURE 5: Volume functions of voids for null threshold and optimal threshold
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}

  \captionof{figure}{\small Volume functions of voids for both web schemes.
  In the upper panel is shown the results for the catalogue generated at
  $\lambda_{th} = 0.0$, while in the lower panel for the catalogue at 
  $\lambda_{th} = \lambda_{opt}$.}

@@

%.........................................................................
%FIGURE 6: Distribution of eigenvalues of the inertia tensor
\begin{flushleft}
\begin{figure*}
\begin{center}

  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Tweb}
  \includegraphics[trim = 7mm 9mm 1mm 0mm, clip, keepaspectratio=true,
  width=0.36\textheight]{./figures/voids_inertia_tensor_Vweb}

  \captionof{figure}{\small Histogram of eigenvalue ratio $\tau_1/\tau_2$
  vs $\tau_2/\tau_3$ for the inertia tensor of void regions. T-web 
  (upper panel) and V-web (lower panel). Number of cells per 
  region in 2D histograms are indicated by the respective colour bar. 
  Upper ($\tau_1/\tau_2$) and right ($\tau_2/\tau_3$) panels of each 
  figure shows a normalized histogram of each ratio parameter. The 
  adopted division for quantify the morphology of void regions is not
  well justified, it should be understood as a fuzzy and continuous 
  limit, done just for illustrative purposes.}

  \label{fig:distro_inertia}
  \vspace{0.1 cm}

\end{center}
\end{figure*}
\end{flushleft}
%.........................................................................

>>>>

Following the recent growing interest in studying galaxy formation in 
low-density regions as cosmological tests, we propose an scheme to find 
bulk voids by using the two defined web schemes. Initially, we explore a 
first simple method based on a FOF-like algorithm, where we build an input 
catalogue for the FOF method with the coordinate of the center of every 
cell marked as void according to the web classification scheme adopted, 
setting a linking length to connect diagonal neighbour cells.

Following the work of \SRKED{Forero-Romero et al. 2008}, we also perform a
percolation analysis in order to select the best threshold parameter that
reduces percolation in cells. In the left panels of the figure 
\ref{fig:percolation_analysis_FOF} we show the result of our percolation 
analysis for both web schemes. In both cases, it can be noticed that the 
volume of the largest void region is minimized at $\lambda_{th} = 0.0$, 
what means that percolation is completely reduced for this threshold 
value. However, according to our previous analysis, such value does not 
reproduce the visual appearance of the cosmic web, so it is out of 
consideration.

%*************************************************************************
\section{Statistics of voids and influence over dark matter halos}
\label{sec:statistics}
%*************************************************************************

@@

%.........................................................................
%FIGURE 1: Fraction of halos in each environment
\begin{flushleft}
\begin{figure}
\centering

@@

\end{figure}
\end{flushleft}
%.........................................................................

@@

  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_regions_percolation_FOF.pdf}
  \includegraphics[trim = 1mm 10mm 8mm 18mm, clip, keepaspectratio=true,
  width=0.25\textheight]{./figures/voids_regions_percolation_LAY.pdf}

@@

%.........................................................................
%FIGURE 5: Percolation analysis for FOF void finder
\begin{flushleft}
\begin{figure*}
\centering

  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_regions_volume_FOF_null.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_regions_volume_FOF_opt.pdf}
  \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, keepaspectratio=true,
  width=0.24\textheight]{./figures/voids_regions_volume_LAY_opt.pdf}

@@

### 2014-04-28 time-machine/cosmic_voids(28-04-14).tex
time machine

Quantifying the shape of voids is gaining importance due to cosmological 
tests such as the Alcock-Paczynski test \SRKED{Sutter, et.al (2012)}, so 
we compute here the reduced inertia tensor through the next expression in 
order to determine shape distributions of bulk voids.

@@

>>>>

Quantifying the shape of voids is gaining importance due to cosmological 
tests such as the Alcock-Paczynski test \SRKED{[Sutter, et.al (2012)]}, so 
we compute here the reduced inertia tensor through the next expression in 
order to determine shape distributions of bulk voids.

@@

Describing the density profiles of voids is quite important in order to 
compare and match simulation with observational surveys, allowing possible
constrains for different cosmology models \SRKED{[Hamaous, et.al 2014]}. 
Here, and taking into account the previous results, we rather use an 
ellipsoidal approximation to describe and fit the shape of bulk voids, so 
we use the next ellipsoidal radial coordinate to describe density profiles.

%.........................................................................
%Ellipsoidal radial coordinate
\eq{radial_coordinate}
{
r^2 = \frac{x^2}{\tau_1^2} + \frac{y^2}{\tau_2^2} + \frac{z^2}{\tau_3^2},
\ \ \ \ 0\leq r \leq 1
}
%.........................................................................
where we take the principal moments of inertia $\{\tau_i \}$ as the 
lengths of the principal axes of the ellipsoid and each one of the 
cartesian coordinates as measured in the rotated frame of each void.

We use the same analytic density profile that \SRKED{[Hamaous, et.al 2014]} 
to fit the numerical density profiles of our voids.

%.........................................................................
%Density profile
\eq{density_profile}
{
\delta_v(r) = \delta_c\frac{1-(r/r_s)^\alpha}{1+(r/r_v)^\beta}
}
%.........................................................................
